%%%%%%%%%%%%%%%%%
% This is a two-column CV template based on moderncv.cls
% (v1.0, May 16 2024) written by Genki Ogaki (rockstarogk@gmail.com). Compiles with XeLaTeX.
%
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%

% environment
\documentclass[11pt]{moderncv}
\moderncvtheme[blue]{banking}
\usepackage{longtable}
\usepackage{marvosym}
\usepackage{array}
\usepackage[T1]{fontenc}
\usepackage{enumitem}
\usepackage{inputenc}
\usepackage{fontawesome5}
\usepackage[scale=0.85, top=0.7in]{geometry}
\usepackage{tabularx}
\usepackage{longtable}
\usepackage{mathpazo}
\usepackage[unicode]{hyperref}
\hypersetup{
    urlbordercolor=cyan,
    linkcolor=black,
    filecolor=magenta,      
    urlcolor=black,
}%
\renewcommand{\baselinestretch}{1} 
% macro

\newcolumntype{L}{>{\raggedright\arraybackslash}X}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}

\newcommand*{\experienceentry}[4][1.5mm]{
    { #2 \hfill} {#3}  \vspace{-0.4mm} \\
    {\itshape {#4}}
    \vspace{-1mm} 
    \par\addvspace{#1}
}

\newcommand*{\educationentry}[5][0.5mm]{
    \begin{tabularx}{\textwidth}{LR}
        {\bfseries #3} & {\bfseries #4} \\
        {\itshape #2} & {#5}
    \end{tabularx}
    
    \par\addvspace{#1}
}

% preamble
\firstname{}
\familyname{Dr.~Alice Lacaze-Masmonteil}
\address{PIMS-CNRS Postdoctoral Fellow}{}

% document
\begin{document}
\maketitle
\vspace{-9.0mm}
\begin{center}
\begin{tabular} {l c l}
    \emailsymbol\enspace \emaillink{Alice.Lacaze-Masmonteil@uregina.ca}& \enspace& \faGlobe\enspace\href{https://alicelacaze-masmonteil.github.io}{https://alicelacaze-masmonteil.github.io} \\
\faPassport\enspace  Canadian and French &  \enspace &Pronouns: She/her
  \end{tabular}
    \end{center}
\vspace{-2.0mm}
% left column
%\begin{minipage}[t]{0.48\textwidth}
\section{Education}
\educationentry{PhD in Mathematics and Statistics}{University of Ottawa}{Ottawa, ON, Canada}{2020-2024}
Advisor: Mateja \v{S}ajna\\
Thesis: Certain resolvable directed cycle decompositions of directed graphs\\
\vspace{-2.0mm}

\educationentry{Master of Science - Mathematics}{Acadia University}{Wolfville, NS, Canada}{2017-2019}
Advisor: Nancy E.~Clarke\\
Thesis: Some problems on the game of Ambush Cops and Robbers\\
\vspace{-2.0mm}

\educationentry{Bachelor of Pure and Applied Sciences}{Acadia University}{Wolfville, NS, Canada}{2012-2016}

\section{Academic Positions}
\educationentry{Pacific Institute for the Mathematical Sciences- Centre National de la Recherche Scientifique (PIMS-CNRS) Postdoctoral Fellow }{University of Regina}{Regina, SK, Canada}{2024-2026}
Advisor: Karen Meagher\\

\vspace{-2.0mm}
\educationentry{Visiting PhD student}{Monash University}{Melbourne, VIC, Australia}{2023}
Advisor: Daniel Horsley
\par

\section{Research Interests}
My main area of research is discrete mathematics. Namely, I am specialized in cycle decomposition problems. 

\section{Publications}
Journal Articles Published
\begin{enumerate}[label={[\arabic*]}]
\setlength\itemsep{0em}
\itemindent=10pt
\item \textbf{ A. Lacaze-Masmonteil}, \href{https://arxiv.org/abs/2410.02109}{Decompositions of the wreath product of certain directed graphs into directed hamiltonian cycles}, to appear in \textit{Ars Mathematicae Contemporanea}.
\item  \textbf{A. Lacaze-Masmonteil}, \href{https://onlinelibrary.wiley.com/doi/abs/10.1002/jcd.21918}{Completing the solution of the directed Oberwolfach problem with cycles of equal length}, \textit{Journal of Combinatorial Designs}, \textbf{ 32} (2024), 5-30.
\end{enumerate}

Journal Articles Under Review

\begin{enumerate}[resume, label={[\arabic*]}]
\setlength\itemsep{0em}
\itemindent=10pt
\item H. Gupta, A. Herman, \textbf{ A.~Lacaze-Masmonteil}, R. Maleki, K.~ Meagher \href{https://arxiv.org/abs/2510.17135}{On the second largest eigenvalue of certain graphs in the perfect matching association scheme}, submitted October 2025. 
\item \textbf{A.~Lacaze-Masmonteil},  \href{https://arxiv.org/abs/2412.13392}{Hamiltonian decompositions of the wreath product of hamiltonian decomposable digraphs}, submitted December 2024.  %to Discrete Mathematics.
\item D.~Horsley and \textbf{A.~Lacaze-Masmonteil}, \href{https://arxiv.org/abs/2408.10448}{Completing the solution of the directed Oberwolfach problem with two tables}, submitted August 2024. %to The Electronic Journal of Combinatorics.
\end{enumerate}

\pagebreak
\section{Fellowships, Prizes, and Scholarships}
 All monetary values are given in Canadian Dollar (CAD). 
 \begin{itemize}
\setlength\itemsep{-0.65em}
\item University of Ottawa Department of Mathematics and Statistics PhD Thesis Award (2025)
  \vspace{-2mm}
\begin{itemize}
    \item Awarded to the best doctoral thesis in the department of mathematics and statistics.
\end{itemize}
\item PIMS-CNRS Postdoctoral Fellowship (2024-2026)
  \vspace{-2mm}
\begin{itemize}
    \item Valued at \$62,000 per year.
\end{itemize}
\item University of Ottawa Mathematics and Statistics Outstanding Student Paper Prize (2023)
  \vspace{-2mm}
\begin{itemize}
    \item Awarded annually to the best paper published by a student.
\end{itemize}
\item Peter Rodney Memorial Book Prize (2023)
  \vspace{-2mm}
\begin{itemize}
    \item Awarded to the best student talk given at the 27th  Ontario Combinatorics Workshop. 
\end{itemize}
\item University of Ottawa André Dabrowski Scholarship Fund (2023)
  \vspace{-2mm}
\begin{itemize}
    \item  Valued at \$1,400. Awarded to a student that demonstrated qualities of leadership.
\end{itemize}
\item Natural Sciences and Engineering Research Council of Canada (NSERC) Michael Smith Foreign Study Supplement (2023)
  \vspace{-2mm}
\begin{itemize}
    \item  National research scholarship valued at \$6,000 to fund visit to Monash University in Melbourne Australia.
\end{itemize}
\item NSERC Canada Graduate Scholarship - Doctoral (2021-2024)
  \vspace{-2mm}
\begin{itemize}
    \item  National research scholarship valued at \$35,000 per year.
\end{itemize}
\item Catherine Stanley Memorial Scholarship (2018)
  \vspace{-2mm}
\begin{itemize}
    \item  Awarded to a student that demonstrated excellence as a teaching assistant.
\end{itemize}
\item NSERC Canada Graduate Scholarship  - Master's program (2017)
  \vspace{-2mm}
\begin{itemize}
    \item  Institutional research scholarship valued at \$17,500.
\end{itemize}
%\item Acadia Undergraduate Mathematics Competition: Best Paper (2016)
\end{itemize}
  \vspace{-6mm}
\section{Mentorship}
Semesters are given in terms of the standard North American academic calendar.  \\
  \vspace{-1mm}

\educationentry{Undergraduate summer students mentor}{University of Regina}{Regina, SK, Canada}{Summer 2025}

Created a seminar series on scientific communication skills for undergraduate summer students in mathematics.
  \vspace{-4mm}

\section{Teaching}  
 \educationentry{Sessional Instructor} {University of Regina} {Regina, SK, Canada}{2024-Present}
 Courses (taught in english):\\
MATH 221:  Introduction to Proofs and Problem Solving \hfill Fall 2025 \\
MATH 223:  Introduction to Abstract Algebra   \hfill Winter 2025 \\
MATH 122: Linear Algebra 1  \hfill Fall 2024 \\

  \vspace{-0.5mm}
 \educationentry{Part-time professor}{University of Ottawa}{Ottawa, ON, Canada}{2023}
Courses (taught in French):  

MAT 1741: Introduction to Linear Algebra  \hfill Winter 2023 
  \vspace{-4mm}
\section{Presentations}

\textbf{Invited Conference Presentations}
  \vspace{-2mm}
\begin{itemize}
\setlength\itemsep{-0.25em}
\item 2025 Canadian Mathematical Society Winter Meeting: Algebraic Graph Theory Scientific Session, Toronto, ON, Canada, (Dec.~2025).
\item10th Cracow Conference on Graph Theory: Design Theory Session, Cracow, Poland, (Sep.~2025).
    \item Canadian Discrete and Algorithmic Mathematics Conference 2025: From Puzzles to Proofs: Connecting the Dots with Combinatorics, Ottawa, ON, Canada, (May 2025).
\item 2024 Canadian Mathematical Society Winter Meeting: Combinatorial Designs Scientific Session, Vancouver, BC, Canada, (Dec.~2024).
\item Banff International Research Station: Movement and Symmetry in Graphs Workshop, Banff, AB, Canada, (Nov.~2024). 
\item 10th Slovenian Conference on Graph Theory: Combinatorial Designs and their Applications Mini Symposium, Kranjska Gora, Slovenia, (June 2023).  
\item 2022 Canadian Mathematical Society Summer Meeting: Design Theory and Graph Decomposition Scientific Session, St. John's, NL, Canada, (June 2022).  
\end{itemize}

\textbf{ Contributed Conference Presentations}
  \vspace{-1mm}
\begin{itemize}
\setlength\itemsep{-0.25em}
\item 2025 Canadian Mathematical Society Winter Meeting: Combinatorial Designs Scientific Session, Toronto, ON, Canada, (Dec.~2025).
    \item Women in Combinatorics Virtual Conference, Online, (July 2024).  
     \item 45th Australasian Combinatorics Conference, Perth, WA, Australia, (Dec.~2023).  
 \item 2023 Canadian Mathematical Society Summer Meeting: Design Theory and Graph Decomposition Session, Ottawa, ON, Canada, (June 2023).  
   \item 27th Ontario Combinatorics Workshop, Ottawa, ON, Canada, (May 2023). 
\item 26th Ontario Combinatorics Workshop, Waterloo, ON, Canada, (May 2022).  
\item 25th Ontario Combinatorics Workshop, Online, (June 2021). 
\end{itemize}  
  \textbf{Seminars}
  \begin{itemize}
\setlength\itemsep{-0.25em}
\item University of Manitoba Department of Mathematics Colloquium, Winnipeg, MB, Canada, (Nov.~2025).
\item University of Victoria Discrete Mathematics Seminar, Victoria, BC, Canada, (Nov.~2025).
\item PIMS Postdoctoral Summit, Calgary, AB, Canada, (Apr.~2025).
\item AARMS  Atlantic Graph Theory Seminar, Online, (Nov.~2024).
\item Lethbridge Number Theory and Combinatorics Seminar Lethbridge, AB, Canada, (Oct.~2024).
\item PIMS Emergent Research: The PIMS Postdoctoral Fellow Seminar, Online, (Oct.~2024).
\item  Monash University Discrete Mathematics Seminar, Melbourne, VIC, Australia, (Oct.~2023).
\end{itemize}
  \vspace{-5mm}

\section{Selected Service}
\textbf{Referee for the following publications}: Australasian Journal of Combinatorics, Journal of Combinatorial Designs, Graphs and Combinatorics, Bulletin of the Institute of Combinatorics and its Applications, Discussiones Mathematicae Graph Theory.\\

\vspace{-2mm}
\experienceentry{2026 Prairie Discrete Mathematics Workshop}{2026}{Co-organizer}
\experienceentry{2025 CMS Winter Meeting}{2025}{Combinatorial Design Theory Session co-organizer}
\experienceentry{Canadian Discrete and Algorithmic Mathematics Conference 2025}{2025}{Women in combinatorics mentorship lunch co-organizer}
\experienceentry{Canadian Discrete and Algorithmic Mathematics Conference 2025}{2025}{Combinatorial Designs and Graph Decompositions Scientific Session co-organizer}
\experienceentry{Pi Day at the Saskatchewan Science Centre}{2025}{Facilitator}
\experienceentry{University of Regina Day - Mathematics Outreach}{2024}{Facilitator}
\experienceentry{Women in Combinatorics Virtual Conference}{2024}{Combinatorial Designs Session co-organizer}
\experienceentry{27th Ontario Combinatorics Conference}{2023}{Co-organizer}
\experienceentry{Canadian Mathematical Society Student Committee}{2022-2024}{Chair}
\experienceentry{UO Mathematics and Statistics Graduate Student Association Executive}{2022-2023}{President}
\experienceentry{Ottawa Mathematics and Statistics Conference}{2021-2023}{Co-organizer}
\vspace{-3mm}
\section{References}
\begin{itemize}
\setlength\itemsep{-0.3em}
    \item Karen Meagher, University of Regina \hfill %\emailsymbol\enspace \emaillink{karen.meagher@uregina.ca}
    \item Daniel Horsley, Monash University \hfill %\emailsymbol\enspace \emaillink{daniel.horsley@monash.edu}
    \item Mateja \v{S}ajna, University of Ottawa \hfill %\emailsymbol\enspace \emaillink{mateja.sajna@uottawa.ca}
    \item Shaun Fallat, University of Regina, (Teaching/service reference) %\hfill \emailsymbol\enspace \emaillink{shaun.fallat@uregina.ca}
\end{itemize}
%\end{minipage}

\end{document}
